### 2015-07-30 Docs/visualization/visualization.tex
add documentation on the mini plotfiles

>>>>

\subsection{Mini vs.\ regular plotfiles}

\maestro\ can manage two independent sets of plotfiles.  This allows you to
output the default plotfiles, which contain a lot of variables, sparsely,
and output mini-plotfiles much more frequently.  A mini-plotfile is controlled
by the analogous runtime parameters as the main plotfiles:

\begin{itemize}
\item {\tt mini\_plot\_int} is the interval in steps between successive plotfiles
\item {\tt mini\_plot\_deltat} is the interval in time between successive plotfiles
\item {\tt mini\_plot\_base\_name} is the base name that prefixes the plotfiles.  The
  default is {\tt miniplt}
\end{itemize}

To set the fields that are stored in the mini plotfile, a second set
of runtime parameters is used: {\tt mini\_plot\_var1}, {\tt
  mini\_plot\_var2}, $\ldots$, {\tt mini\_plot\_var9}.  These can be set to
any of the following:
\begin{itemize}
  \item {\tt "density"}
  \item {\tt "species"}: this gets all of the mass fractions
  \item the name of an individual species in the network (like {\tt "helium-4"})
  \item {\tt "radvel"}: this gets both the radial and circumferential velocity
  \item {\tt "velocity"}: all three componets
  \item {\tt "temperature"}: this is either $T(\rho,p_0)$ or $T(\rho,h)$, depending
    on the value of {\tt use\_tfromp}
  \item {\tt "enuc"}: the nuclear energy generation rate
  \item {\tt "mach"}: the Mach number
\end{itemize}
